Results_setup

### 2020-06-19 data/SetupData.Rmd
updating data files after removing outlier, fix fig3

opts_knit$set(root.dir = "~./MLH1repo/")
setwd("~./MLH1repo/")

@@

#MLH1_data = read.csv(here("data", "/AnonData.csv"), sep="\t", header=TRUE)
#read.csv was breaking things
MLH1_data = read.xlsx2("~./MLH1repo/data/AnonData_formated.xlsx", header=TRUE, 1)
#remove all X's from MLH1, remove all old mice?
#add date imaged
#remove the Remove mice, (juvi, old, bad quality)

@@

#total SC 
#new total_SC == will have all of the Batches

@@

#Total.SC_DF = read.xlsx2("~./MLH1repo/data/Total.SC_DF.xlsx", header=TRUE, 1)

#original Curate_bivata + missing SKIVE female
Curated_BivData <-  read.csv2("~./MLH1repo/data/Curated_BivData_5.30.20.csv", sep=" ", header=TRUE)
#why they fuck was this space deliminated? I hate excel uggg

@@

```{r MLH1.DF.setup, warning=FALSE, echo=FALSE}

@@

`r length(original_DF_duplicates$Random.Name)` rows are marked as duplicate.  `r length(original_DF_duplicates$fileName)` rows (images) have been counted across mulitple batches. These are removed in the MLH1_data DF.

```{r clean_MLH1_data, echo=FALSE}
#Clean up main DF, MLH1_data
#remove duplicated data from MLH1 -- remove 1 or the two rows
#https://www.datanovia.com/en/lessons/identify-and-remove-duplicate-data-in-r/
#use distinct() in dlpyr()
MLH1_data <- MLH1_data %>% distinct(Original.Name, .keep_all = TRUE)#5216 to 4983

@@

`r length(original_DF$fileName[ grepl("X", original_DF$X)] )` images (rows) have X's, they are removed from the main dataset.

@@

                    'SPRET'='gold','SPIC'= 'goldenrod1', #browns? color of mounds?
                    'CAROLI'='gold3',

@@

The original dataset was cleaned up in the following ways before analysis. Settting up main data file with explanation and examination of data. Make the raw original DF and main working DF with bad cells exlcuede. The original dataset had `r length(original_DF_duplicates$fileName)` duplicated file names. These were removed and can be used to quantify repeatability or repair. Using the distinct() function for the MLH1_data, the first duplicated filename is kept and the second removed.

@@

#write excel file
#write.xlsx2(missing.SKIVE.female, "Curated_missing.SKIVE.female.xlsx", sheetName = "Sheet1", 
#            col.names = TRUE, row.names = FALSE, append = FALSE)

@@

```{r clean.total.sc, echo=FALSE}
#everything are factors again
#clean
Total.SC_DF$notes <- as.character(Total.SC_DF$notes)
Total.SC_DF$REDO.crop <- as.character(Total.SC_DF$REDO.crop)

@@

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_5.30.20.RData")

>>>>

opts_knit$set(root.dir = "~./MLH1repo/data/")
setwd("~./MLH1repo/data/")

@@

#MLH1_data = read.csv(here("data", "/AnonData.csv"), sep="\t", header=TRUE)
#read.csv was breaking things
MLH1_data = read.xlsx2("~./MLH1repo/data/MLH1.AnonData_formated.xlsx", header=TRUE, 1)
#remove all X's from MLH1, remove all old mice?
#add date imaged
#remove the Remove mice, (juvi, old, bad quality)

@@

@@

#this file is missing
Curated_BivData <-  read.csv2("~./MLH1repo/data/Curated_BivData_5.30.20.csv", sep=" ", header=TRUE)
#why they fuck was this space deliminated? I hate excel uggg

@@

```{r MLH1.DF.setup, warning=FALSE, echo=FALSE, eval=FALSE}

#duplicate file names and rows have been removed
#they can be found in older files for accuracy checks

#check that these should all be redundant

@@

```{r clean_MLH1_data, echo=FALSE}
#Clean up main DF, MLH1_data
#remove duplicated data from MLH1 -- remove 1 or the two rows
#https://www.datanovia.com/en/lessons/identify-and-remove-duplicate-data-in-r/

#use distinct() in dlpyr()
MLH1_data <- MLH1_data %>% distinct(Original.Name, .keep_all = TRUE)#5216 to 4983

@@

@@

                    'SPRET'='gold','SPI'= 'goldenrod1', #browns? color of mounds?
                    'CAROLI'='gold3',

@@

The original dataset was cleaned up in the following ways before analysis. Settting up main data file with explanation and examination of data. Make the raw original DF and main working DF with bad cells exlcuede. The original dataset had a number of duplicated file names. These were removed and can be used to quantify repeatability or repair. Using the distinct() function for the MLH1_data, the first duplicated filename is kept and the second removed.

@@

#write excel file
#write.xlsx2(XX, "XX.xlsx", sheetName = "Sheet1", 
#            col.names = TRUE, row.names = FALSE, append = FALSE)

@@

```{r clean.total.sc, echo=FALSE}
#everything are factors again
#clean
#Total.SC_DF$notes <- as.character(Total.SC_DF$notes)
Total.SC_DF$REDO.crop <- as.character(Total.SC_DF$REDO.crop)

@@

#20feb16_G_f2

@@

save.image("~./MLH1repo/data/MLH1_data_setup_5.30.20.RData")

### 2020-06-19 src/Result_Setup.Rmd
updating data files after removing outlier, fix fig3

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
library(raster)
library(lme4)
library(nlme)
library(RLRsim)
library(ggpubr)
library(reshape2)
#library(patchwork)

@@

#MLH1_data <- with(MLH1_data, MLH1_data[order(category),])
AP_mouse_table.HQ$var <- as.numeric(AP_mouse_table.HQ$var)

@@

```{r MLH1.FEMALE.TABLE, echo=FALSE, eval=TRUE}

female_mouse.avs_for.analysis <-  Mouse.Table_HQ %>% filter(sex== "female") %>% filter(species == "M.musculus")

@@

127 mice, 8 strains (correct), 0 MOLF females!

@@

@@

write.table(summ.MLH1.M2.glm.strain.fixed.full$coefficients , "~./MLH1repo/MLH1_M2_glm.csv", sep=",",row.names = TRUE)
```

```{r MLH1.glm.M3, echo=FALSE, eval=TRUE}

MLH1.M3.strain.fixed <- glm(mean_co ~ sex * strain, data=DF.HetC.MixedModel.HQ )

summ.MLH1.M3.strain.fixed <- summary(MLH1.M3.strain.fixed)

@@

write.table(summ.MLH1.M3.strain.fixed$coefficients , "~./MLH1repo/MLH1_M3_glm.csv", sep=",",row.names = TRUE)
```

@@

@@

write.table(sum_MLH1.female.spc.glm.M5$coefficients, "~./MLH1repo/MLH1_M5_female_glm.csv", sep=",",row.names = TRUE)
```

@@

write.table(sum_MLH1.male.glm.M4$coefficients , "~./MLH1repo/MLH1_M4_male_glm.csv", sep=",",row.names = TRUE)

#M4.2
MLH1.male.glm.M4.2 <- glm(mean_co ~ strain, data= (male_mouse.avs_for.analysis  %>% filter(subsp != "Cast") ))
sum_MLH1.male.glm.M4.2 <- summary(MLH1.male.glm.M4.2)

@@

write.table(sum_MLH1.male.glm.M4.2$coefficients , "~./MLH1repo/MLH1_M5_male_glm.csv", sep=",",row.names = TRUE)

#MLH1 variance models

**THIS IS BEING MOVED TO CHAPTER 3**

M1 - subsp, sex, (1 | strain)  (lmer)
M2 - subsp, sex, strain  (glm / lm?)
M3 - sex, strain
M4 - strain (sex specific)

```{r M1.MLH1.var_cv, echo=FALSE, warning=FALSE, message=FALSE}
MLH1var_M1 <- lmer( var ~ subsp * sex +(1|strain), data= (DF.HetC.MixedModel.HQ %>% filter(species == "M.musculus"))   )
MLH1var_M1.reduce.sex <- lmer( var ~ subsp  +(1|strain), data= (DF.HetC.MixedModel.HQ %>% filter(species == "M.musculus")) )
MLH1var_M1.reduce.subp <- lmer( var ~ sex  +(1|strain), data= (DF.HetC.MixedModel.HQ %>% filter(species == "M.musculus")) )

#summary(MLH1var_M1)
LmerMLH1_VAR_int <- drop1(MLH1var_M1, test="Chisq")$`Pr(Chi)`[2]
LmerMLH1_VAR_sex <- anova(MLH1var_M1, MLH1var_M1.reduce.sex)$`Pr(>Chisq)`[2]
LmerMLH1_VAR_subsp <- anova(MLH1var_M1, MLH1var_M1.reduce.subp)$`Pr(>Chisq)`[2]
LmerMLH1_VAR_strain <- exactRLRT(MLH1var_M1)$p.value

LmerMLH1_VAR_results <- data.frame(sub.sp = LmerMLH1_VAR_subsp,
sex.results =  LmerMLH1_VAR_sex, interaction.pval = LmerMLH1_VAR_int,  rand.pval = LmerMLH1_VAR_strain)

#CV
MLH1cV_M1 <- lmer( cV ~ subsp * sex +(1|strain), data=DF.HetC.MixedModel.HQ )
MLH1cV_M1.reduce.sex <- lmer( cV ~ subsp  +(1|strain), data=DF.HetC.MixedModel.HQ )
MLH1cV_M1.reduce.subp <- lmer( cV ~ sex  +(1|strain), data=DF.HetC.MixedModel.HQ )

LmerMLH1_CV_int <- drop1(MLH1cV_M1, test="Chisq")$`Pr(Chi)`[2]
LmerMLH1_CV_sex <- anova(MLH1cV_M1, MLH1cV_M1.reduce.sex)$`Pr(>Chisq)`[2]
LmerMLH1_CV_subsp <- anova(MLH1cV_M1, MLH1cV_M1.reduce.subp)$`Pr(>Chisq)`[2]
LmerMLH1_CV_strain <- exactRLRT(MLH1cV_M1)$p.value

LmerMLH1_CV_results <- data.frame(sub.sp = LmerMLH1_CV_subsp,
sex.results =  LmerMLH1_CV_sex, interaction.pval = LmerMLH1_CV_int,  rand.pval = LmerMLH1_CV_strain)

#Q12
Q12_mouse_table_MLH1$subsp <- factor(Q12_mouse_table_MLH1$subsp, ordered = FALSE)
Q12_mouse_table_MLH1$sex <- factor(Q12_mouse_table_MLH1$sex, ordered = FALSE)
Q12_mouse_table_MLH1$strain <- factor(Q12_mouse_table_MLH1$strain, ordered = FALSE)
Q12_mouse_table_MLH1$species <- factor(Q12_mouse_table_MLH1$species, ordered = FALSE)

#USE Q12 (Q123) table
#Q12_mouse_table_w.Ages
#Q12 var
MLH1var_M1_Q12 <- lmer( var ~ subsp * sex +(1|strain), data=(Q12_mouse_table_MLH1 %>% filter(species == "M.musculus")) )
MLH1var_M1_Q12reduce.sex <- lmer( var ~ subsp  +(1|strain), data=(Q12_mouse_table_MLH1 %>% filter(species == "M.musculus")) )
MLH1var_M1_Q12reduce.subp <- lmer( var ~ sex  +(1|strain), data=(Q12_mouse_table_MLH1 %>% filter(species == "M.musculus")) )

LmerMLH1_M1_Q12VAR_int <- drop1(MLH1var_M1_Q12, test="Chisq")$`Pr(Chi)`[2]
LmerMLH1_M1_Q12_VAR_sex <- anova(MLH1var_M1_Q12, MLH1var_M1_Q12reduce.sex)$`Pr(>Chisq)`[2]
LmerMLH1_M1_Q12_VAR_subsp <- anova(MLH1var_M1_Q12, MLH1var_M1_Q12reduce.subp)$`Pr(>Chisq)`[2]
LmerMLH1_M1_Q12_VAR_strain <- exactRLRT(MLH1var_M1_Q12)$p.value

LmerMLH1_M1_Q12_VAR_results <- data.frame(sub.sp = LmerMLH1_M1_Q12_VAR_subsp,
sex.results =  LmerMLH1_M1_Q12_VAR_sex, interaction.pval = LmerMLH1_M1_Q12VAR_int,  rand.pval = LmerMLH1_M1_Q12_VAR_strain)

#Q12 cv
MLH1cv_M1_Q12 <- lmer( cV ~ subsp * sex +(1|strain), data=Q12_mouse_table_w.Ages )
MLH1cv_M1_Q12reduce.sex <- lmer( cV ~ subsp  +(1|strain), data=Q12_mouse_table_w.Ages )
MLH1cv_M1_Q12reduce.subp <- lmer( cV ~ sex  +(1|strain), data=Q12_mouse_table_w.Ages )

LmerMLH1_M1_Q12_CV_int <- drop1(MLH1cv_M1_Q12, test="Chisq")$`Pr(Chi)`[2]
LmerMLH1_M1_Q12_CV_sex <- anova(MLH1cv_M1_Q12, MLH1cv_M1_Q12reduce.sex)$`Pr(>Chisq)`[2]
LmerMLH1_M1_Q12_CV_subsp <- anova(MLH1cv_M1_Q12, MLH1cv_M1_Q12reduce.subp)$`Pr(>Chisq)`[2]
LmerMLH1_M1_Q12_CV_strain <- exactRLRT(MLH1cv_M1_Q12)$p.value

LmerMLH1_M1_Q12_VAR_results <- data.frame(sub.sp = LmerMLH1_M1_Q12_CV_subsp,
sex.results =  LmerMLH1_M1_Q12_CV_sex, interaction.pval = LmerMLH1_M1_Q12_CV_int,  rand.pval = LmerMLH1_M1_Q12_CV_strain)
```

```{r M2.MLH1.var, echo=FALSE, include=FALSE}

MLH1var_M2 <- glm( var ~ subsp * sex * strain,  data= ( DF.HetC.MixedModel.HQ %>% filter(species == "M.musculus") )  )
MLH1var_M2_sum <- summary(MLH1var_M2)

MLH1var_M2_sum_coE <- as.data.frame( round(summary(MLH1var_M2)$coefficients, 6)) #table of p values for coefficients.

MLH1cv_M2 <- glm(cV ~ subsp*sex*strain, data=DF.HetC.MixedModel.HQ)
#summary(MLH1cv_M2)
#anova(MLH1cv_M2)
#as.data.frame( round(summary(MLH1cv_M2)$coefficients, 6))

#Q12 var
MLH1var_M2_Q12 <- glm( var ~ subsp*sex*strain,  data= (Q12_mouse_table_MLH1 %>% filter(species == "M.musculus")) )
sum.MLH1var_M2_Q12 <- summary(MLH1var_M2_Q12)
sum.MLH1var_M2_Q12.co_eff <- as.data.frame( round(summary(MLH1var_M2_Q12)$coefficients, 6))

#Q12 cv
MLH1cv_M2_Q12 <- glm( cV ~ subsp*sex*strain, data=Q12_mouse_table_w.Ages )
#summary(MLH1cv_M2_Q12)
#anova(MLH1cv_M2_Q12)#sex large F
#as.data.frame( round(summary(MLH1cv_M2_Q12)$coefficients, 6))
```

```{r M3.MLH1.var, echo=FALSE}

glmMLH1Var_M3 <- glm( var ~ sex * strain,  data= (DF.HetC.MixedModel.HQ %>% filter(species == "M.musculus") ) )

glmMLH1Var_M3_sum <- summary(glmMLH1Var_M3)

glmMLH1Var_M3_sum.Coef <- round(glmMLH1Var_M3_sum$coefficients[,c(1,4)], 5)

MLH1cv_M3 <- glm(cV ~ sex * strain, data=DF.HetC.MixedModel.HQ)
#summary(MLH1cv_M4)
#round(summary(MLH1cv_M3)$coefficients[,c(1,4)], 6)

### Q12 var
MLH1var_M3_Q12 <- glm( var ~ sex*strain, data=(Q12_mouse_table_MLH1 %>% filter(species == "M.musculus")) )
MLH1var_M3_Q12_sum <- summary(MLH1var_M3_Q12)

#as.data.frame( round(summary(MLH1var_M3_Q12)$coefficients[,c(1,4)], 6))
#round(summary(MLH1var_M3_Q12)$coefficients[,c(1,4)], 6)

#Q12 cv
MLH1cv_M4_Q12 <- glm( cV ~ sex*strain, data=Q12_mouse_table_w.Ages )
#round(summary(MLH1cv_M4_Q12)$coefficients[,c(1,4)], 6)
```

```{r MLH1.var.M4, echo=FALSE, eval=F}
#male
glmMLH1Var_M4.male <- glm( var ~ subsp * strain,  data= (DF.HetC.MixedModel.HQ %>% filter(sex == "male") ) )

#female
glmMLH1Var_M4.female <- glm( var ~ subsp * strain,  data= (DF.HetC.MixedModel.HQ %>% filter(sex == "female") ) )
sum.glmMLH1Var_M4.female <- summary(glmMLH1Var_M4.female)

glmMLH1Var_M4.femaleQ12 <- glm( var ~ subsp * strain,  data= (Q12_mouse_table_w.Ages %>% filter(sex == "female") ) )

```{r FEMALE.VAR.MODELS, echo=FALSE, eval=F}
## within mouse variance models 
lmVAR.female.strain.subsp <- glm(var ~ subsp * strain, data= female_mouse.avs_for.analysis)
summry.female.strain.VAReffects <- summary(lmVAR.female.strain.subsp)

lmVAR.female.strain <- glm(var ~ strain, data= female_mouse.avs_for.analysis)
lmVAR.female.strain_sum <- summary(lmVAR.female.strain)

#round( #round isn't working for this sumary
#lmVAR.female.strain_sum$coefficients[,c(1,4)]
#Q12
Q12_female_table <-  Q12_mouse_table_w.Ages %>% filter(sex == "female")

lm.m1.Q12_female <- glm(var ~ subsp * strain, data= Q12_female_table)
lm.m1.Q12_female_sum <- summary(lm.m1.Q12_female)

lm.m2.Q12_female <- glm(var ~ strain, data= Q12_female_table)
lm.m2.Q12VAR.female_sum <- summary(lm.m2.Q12_female)#LEW changes to PWD

lm.m2.Q12_female.cv <- glm(cV ~ strain, data= Q12_female_table)
lm.m2.Q12_female.cv_sum <- summary(lm.m2.Q12_female.cv)

#lm.m2.Q12VAR.female_sum$coefficients[,c(1,4)]
#LEW sig

```{r MALE.SPECIFIC.variance.model, echo=FALSE, eval=F}
## within mouse variance models 
lmVAR.male.strain.subsp <- glm(var ~ subsp * strain, data= just.male_mouse.av)
summry.male.strain.VAReffects <- summary(lmVAR.male.strain.subsp)
#round(summry.male.strain.VAReffects$coefficients[,c(1,4)], 5)

#all p values kinda high, MSM and TOM are slightly sig
lmVAR.male.strain <- glm(var ~ strain, data= just.male_mouse.av)
lmVAR.male.strain_sum <- summary(lmVAR.male.strain)
#round(lmVAR.male.strain_sum$coefficients[,c(1,4)], 5)
#non sig

lmcv.male.strain <- glm(cV ~ strain, data= just.male_mouse.av)
lmcv.male.strain_sum <- summary(lmcv.male.strain)
#round(lmcv.male.strain_sum$coefficients[,c(1,4)], 5)
#HMI sig for cv model -- in the other model, CAST subsp and TOM strain are slightly significant

#Q12
Q12_male_table <-  Q12_mouse_table_w.Ages %>% filter(sex == "male")

lm.m1.Q12_male <- glm(var ~ subsp * strain, data= Q12_male_table)
lm.m1.Q12_male_sum <- summary(lm.m1.Q12_male)
#round(lm.m1.Q12_male_sum$coefficients[,c(1,4)], 5)
#NS

lm.m2.Q12_male <- glm(var ~ strain, data= Q12_male_table)
lm.m2.Q12VAR.male_sum <- summary(lm.m2.Q12_male)
#round(lm.m2.Q12VAR.male_sum$coefficients[,c(1,4)], 5)
#NS

@@

@@

#sex most sig
#subsp

#straing G, LEW
#mol * sex
#G * sex

@@

@@

#LOT OF SIGNIFICant strain effects in this model
write.table(sum.Q1.glm_totSC_M3$coefficients, "~./MLH1repo/TotalSC_Q1_M3.csv", sep=",",row.names = TRUE)
```

@@

#Q1lmer.MM_SC_short_results
write.table(Q1lmer.MM_SC_short_results, "~./MLH1repo/ShortSC_Q1_M1.csv", sep=",",row.names = TRUE)
```

@@

@@

write.table(summ.Q1.glm_short.SC_M2$coefficients, "~./MLH1repo/ShortSC_Q1_M2.csv", sep=",",row.names = TRUE)
```

@@

write.table(summ.Q1.glm_short.SC_M3$coefficients, "~./MLH1repo/ShortSC_Q1_M3.csv", sep=",",row.names = TRUE)
```

@@

@@

@@

@@

@@

@@

@@

write.table(summry.glm.Q1_IFD.PER.M2$coefficients, "~./MLH1repo/PER.IFD_Q1_M2.csv", sep=",",row.names = TRUE)
```

@@

@@

@@

glm.Q1_IFD.PER.M5.male  <- glm(mean_IFD.2CO_PER ~  strain, data= (mouse.level.BivData_table %>% filter(sex == "male") ) )
summry.glm.Q1_IFD.PER.M5.male  <- summary(glm.Q1_IFD.PER.M5.male)

>>>>

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
library(raster)
library(lme4)
library(nlme)
library(RLRsim)
library(ggpubr)
library(reshape2)
library(writexl)
library(xlsx)
#library(patchwork)

@@

#MLH1_data <- with(MLH1_data, MLH1_data[order(category),])
#AP_mouse_table.HQ$var <- as.numeric(AP_mouse_table.HQ$var)

@@

```{r MLH1.FEMALE.TABLE, echo=FALSE, eval=TRUE}
female_mouse.avs_for.analysis <-  Mouse.Table_HQ %>% filter(sex== "female") %>% filter(species == "M.musculus")

@@

127 mice, 8 strains (correct), 0 MOLF females! -- this was fixed

@@

#goal get all the results below to a .tex format
#write_xlsx(MLH1.MMlmer_results, "~./MLH1repo/MLH1_M1_glm.xlsx", col_names = TRUE)

write.xlsx(MLH1.MMlmer_results, "MLH1_M1_glm.xlsx", col.names = TRUE)
```

@@

write.table(summ.MLH1.M2.glm.strain.fixed.full$coefficients, "~./MLH1repo/MLH1_M2_glm.csv", sep=",",row.names = TRUE)

summary.glm(MLH1.M2.glm.strain.fixed.full)$coefficients

write.xlsx(as.data.frame(summary.glm(MLH1.M2.glm.strain.fixed.full)$coefficients), "MLH1_M2_glm.xlsx", col.names = TRUE, row.names = TRUE)

```{r MLH1.glm.M3, echo=FALSE, eval=TRUE}
MLH1.M3.strain.fixed <- glm(mean_co ~ sex * strain, data=DF.HetC.MixedModel.HQ )
summ.MLH1.M3.strain.fixed <- summary(MLH1.M3.strain.fixed)

@@

write.table(summ.MLH1.M3.strain.fixed$coefficients, "~./MLH1repo/MLH1_M3_glm.csv", sep=",",row.names = TRUE)

#this table wont write!!
write.xlsx(as.data.frame(summary(MLH1.M3.strain.fixed)$coefficients), "MLH1_M3_glm.xlsx", col.names = TRUE, row.names = TRUE)
```

@@

write.xlsx(as.data.frame( summry.female.strain.effects$coefficients), "MLH1_M4_female_glm.xlsx", col.names = TRUE, row.names = TRUE)

@@

write.table(sum_MLH1.female.spc.glm.M5$coefficients, "~./MLH1repo/MLH1_M5_female_glm.csv", sep=",",row.names = TRUE)

write.xlsx(as.data.frame( sum_MLH1.female.spc.glm.M5$coefficients), "MLH1_M5_female_glm.xlsx", col.names = TRUE, row.names = TRUE)
```

@@

write.table(sum_MLH1.male.glm.M4$coefficients, "~./MLH1repo/MLH1_M4_male_glm.csv", sep=",",row.names = TRUE)

write.xlsx(as.data.frame(sum_MLH1.male.glm.M4$coefficients), "MLH1_M4_male_glm.xlsx", col.names = TRUE, row.names = TRUE)

#write_xlsx(sum_MLH1.female.spc.glm.M5$coefficients, #"MLH1_M5_female_glm.xlsx", col_names = TRUE)

#M5
MLH1.male.glm.M5 <- glm(mean_co ~ strain, data= (male_mouse.avs_for.analysis  %>% filter(subsp != "Cast") ))
sum_MLH1.male.glm.M5 <- summary(MLH1.male.glm.M5)

@@

write.table(sum_MLH1.male.glm.M5$coefficients, "~./MLH1repo/MLH1_M5_male_glm.csv", sep=",",row.names = TRUE)

write.xlsx(as.data.frame( sum_MLH1.male.glm.M5$coefficients), "MLH1_M5_male_glm.xlsx", col.names = TRUE, row.names = TRUE)

#write_xlsx(sum_MLH1.male.glm.M4.2$coefficients, "~./MLH1repo/MLH1_M5_male_glm.xlsx", col_names = TRUE)
```

@@

#write_xlsx(Q1.lmer_totSC_M1_results, "~./MLH1repo/TotalSC_Q1_M1.xlsx", col_names = TRUE)

write.xlsx(Q1.lmer_totSC_M1_results, "TotalSC_Q1_M1.xlsx", col.names = TRUE)
```

@@

#sex most sig  #subsp
#straing G, LEW
#mol * sex
#G * sex

@@

write.xlsx(as.data.frame(summary.glm(Q1.glm_totSC_M2)$coefficients), "TotalSC_Q1_M2.xlsx", col.names = TRUE, row.names = TRUE)

#write_xlsx(sum.Q1.glm_totSC_M2$coefficients, "~./MLH1repo/TotalSC_Q1_M2.xlsx", col_names = TRUE)
```

@@

#LOT OF SIGNIFICant strain effects in this model
write.table(sum.Q1.glm_totSC_M3$coefficients, "~./MLH1repo/TotalSC_Q1_M3.csv", sep=",",row.names = TRUE)

#not working currently.. might be same 'ol error
#write.xlsx(  as.data.frame( summary(sum.Q1.glm_totSC_M3)$coefficients ), "TotalSC_Q1_M3.xlsx", col.names = TRUE, row.names = TRUE)

#write_xlsx(sum.Q1.glm_totSC_M3$coefficients, "~./MLH1repo/TotalSC_Q1_M3.xlsx", col_names = TRUE)
```

@@

#Q1lmer.MM_SC_short_results
write.table(Q1lmer.MM_SC_short_results, "~./MLH1repo/ShortSC_Q1_M1.csv", sep=",",row.names = TRUE)

#write_xlsx(Q1lmer.MM_SC_short_results, "~./MLH1repo/ShortSC_Q1_M1.xlsx", col_names = TRUE)

write.xlsx(Q1lmer.MM_SC_short_results, "ShortSC_Q1_M1.xlsx", col.names = TRUE)

@@

write_xlsx(Q1.lmer_short_M1_results, "~./MLH1repo/ShortSC_Q1_M1.xlsx", col_names = TRUE)
```

@@

write.table(summ.Q1.glm_short.SC_M2$coefficients, "~./MLH1repo/ShortSC_Q1_M2.csv", sep=",",row.names = TRUE)

#write_xlsx(summ.Q1.glm_short.SC_M2$coefficients, "~./MLH1repo/ShortSC_Q1_M2.xlsx", col_names = TRUE)

write.xlsx( as.data.frame( summ.Q1.glm_short.SC_M2$coefficients) , "ShortSC_Q1_M2.xlsx", col.names = TRUE, row.names = TRUE)
```

@@

write.table(summ.Q1.glm_short.SC_M3$coefficients, "~./MLH1repo/ShortSC_Q1_M3.csv", sep=",",row.names = TRUE)

write.xlsx(as.data.frame( summ.Q1.glm_short.SC_M3$coefficients), "ShortSC_Q1_M3.xlsx", col.names = TRUE, row.names = TRUE)

@@

#write_xlsx(lmer.Q1.nrm1CO_M1_results, "~./MLH1repo/Nrm1CO_Pos_Q1_M1.xlsx", col_names = TRUE)

write.xlsx(lmer.Q1.nrm1CO_M1_results, "Nrm1CO_Pos_Q1_M1.xlsx", col.names = TRUE, row.names = TRUE)
```

@@

write.xlsx(summry.Q1.glm_F1pos_M2$coefficients, "Nrm1CO_Pos_Q1_M2.xlsx", col.names = TRUE)

#write_xlsx(summry.Q1.glm_F1pos_M2$coefficients, "~./MLH1repo/Nrm1CO_Pos_Q1_M2.xlsx", col_names = TRUE)

@@

write.xlsx(summry.Q1.glm_1CO.pos_M3$coefficients, "Nrm1CO_Pos_Q1_M3.xlsx", col.names = TRUE)

#write_xlsx(summry.Q1.glm_1CO.pos_M3$coefficients, "~./MLH1repo/Nrm1CO_Pos_Q1_M3.xlsx", col_names = TRUE)
```

@@

write_xlsx(Q1.IFD.ABS_M1_lmer.results, "~./MLH1repo/ABS.IFD_Q1_M1.xlsx", col_names = TRUE)

@@

write_xlsx(Q1.IFD.PER_M1_lmer.results, "~./MLH1repo/PER.IFD_Q1_M1.xlsx", col_names = TRUE)

@@

write.xlsx(summry.glm.Q1_IFD.ABS.M2$coefficients, "ABS.IFD_Q1_M2.xlsx", col.names = TRUE)

#write_xlsx(summry.glm.Q1_IFD.ABS.M2$coefficients, "~./MLH1repo/ABS.IFD_Q1_M2.xlsx", col_names = TRUE)

@@

write.table(summry.glm.Q1_IFD.PER.M2$coefficients, "~./MLH1repo/PER.IFD_Q1_M2.csv", sep=",",row.names = TRUE)

write.xlsx(summry.glm.Q1_IFD.PER.M2$coefficients, "PER.IFD_Q1_M2.xlsx", col.names = TRUE)

#write_xlsx(summry.glm.Q1_IFD.PER.M2$coefficients, "~./MLH1repo/PER.IFD_Q1_M2.xlsx", col_names = TRUE)
```

@@

write.xlsx(summry.glm.Q1_IFD.ABS.M3$coefficients, "ABS.IFD_Q1_M3.xlsx", col.names = TRUE)

#write_xlsx(summry.glm.Q1_IFD.ABS.M3$coefficients, "~./MLH1repo/ABS.IFD_Q1_M3.xlsx", col_names = TRUE)

@@

write.xlsx(summry.glm.Q1_IFD.PER.M3$coefficients, "PER.IFD_Q1_M3.xlsx", col.names = TRUE)

#write_xlsx(summry.glm.Q1_IFD.PER.M3$coefficients, "~./MLH1repo/PER.IFD_Q1_M3.xlsx", col_names = TRUE)

@@

glm.Q1_IFD.PER.M5.male  <- glm(mean_IFD.2CO_PER ~  strain, data= (mouse.level.BivData_table %>% filter(sex == "male") ) )
summry.glm.Q1_IFD.PER.M5.male  <- summary(glm.Q1_IFD.PER.M5.male)
```
